Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-07 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Work some on agreement between metrics

>>>>

Here is some analysis of agreement and disagreement among different metrics:

```{r echo = FALSE, results = "asis"}
all_exp <- dist_exp %>%
        full_join(rain_exp, by = c("storm_id", "fips")) %>%
        full_join(wind_exp, by = c("storm_id", "fips")) %>%
        gather(metric, exposure, -storm_id, -fips) %>%
        mutate(exposure = !is.na(exposure)) %>%
        spread(metric, exposure)

check_agreement <- function(data, x1, x2, n_counties = 2396){
        data$x1 <- data[ , x1]
        data$x2 <- data[ , x2]
        agreement <- data %>%
                dplyr::select(storm_id, x1, x2) %>%
                dplyr::mutate(agree_exp = x1 & x2,
                              x1_exp_x2_unexp = x1 & !x2,
                              x1_unexp_x2_exp = !x1 & x2,
                              any_exp = x1 | x2) %>%
                dplyr::group_by(storm_id) %>%
                dplyr::summarize(disagree = sum(!agree_exp),
                                 agree = (n_counties - disagree),
                                 agree_exp = sum(agree_exp),
                                 agree_unexp = (n_counties - disagree - agree_exp),
                                 disagree_x1_exp = sum(x1_exp_x2_unexp),
                                 disagree_x2_exp = sum(x1_unexp_x2_exp),
                                 agree_any = round(100 * agree_exp / sum(any_exp), 1),
                                 disagree_any_x1_exp = round(100 * disagree_x1_exp /
                                                                     sum(any_exp), 1),
                                 disagree_any_x2_exp = round(100 * disagree_x2_exp /
                                                                     sum(any_exp), 1))
        agreement[ , 2:7] <- round(100 * agreement[ , 2:7] / n_counties, 1)
        return(agreement)
}

summarize_agreement <- function(agreement){
        med_val <- apply(agreement[ , -1], MARGIN = 2, FUN = median, na.rm = TRUE)
        min_val <- apply(agreement[ , -1], MARGIN = 2, FUN = min, na.rm = TRUE)
        max_val <- apply(agreement[ , -1], MARGIN = 2, FUN = max, na.rm = TRUE)
        min_storm <- apply(agreement[ , -1], MARGIN = 2,
                           FUN = function(x){
                                   i <- which.min(x)
                                   out <- agreement$storm_id[i]
                                   return(out)
                                   })
        max_storm <- apply(agreement[ , -1], MARGIN = 2,
                           FUN = function(x){
                                   i <- which.max(x)
                                   out <- agreement$storm_id[i]
                                   return(out)
                           })
        out <- rbind(t(as.data.frame(med_val)), t(as.data.frame(min_val)),
                     t(as.data.frame(max_val)), t(as.data.frame(min_storm)),
                     t(as.data.frame(max_storm)))
        out <- as.data.frame(out)
        out$metric <- row.names(out)
        return(out)
}

exp_metrics <- c("dist_exposed", "rain_exposed", "wind_exposed")

agg_exp_matrix <- matrix(NA, ncol = length(exp_metrics), nrow = length(exp_metrics))
colnames(agg_exp_matrix) <- rownames(agg_exp_matrix) <- exp_metrics
agg_unexp_matrix <- x1_exp_matrix <- x2_exp_matrix <- agg_exp_matrix
for(i in 1:length(exp_metrics)){
        for(j in 1:length(exp_metrics)){
                x1 <- exp_metrics[i]
                x2 <- exp_metrics[j]
                # if(x1 == x2) next

                agreement <- check_agreement(all_exp, x1 = x1, x2 = x2)
                agg_exp_matrix[i, j] <- median(agreement$agree_exp, na.rm = TRUE)
                agg_unexp_matrix[i, j] <- median(agreement$agree_unexp, na.rm = TRUE)
                x1_exp_matrix[i, j] <- median(agreement$disagree_x1_exp, na.rm = TRUE)
                x2_exp_matrix[i, j] <- median(agreement$disagree_x2_exp, na.rm = TRUE)
        }
}

out <- rbind(cbind(agg_exp_matrix, x1_exp_matrix),
             cbind(x2_exp_matrix, agg_unexp_matrix)) 
row.names(out) <- NULL
colnames(out) <- NULL
out <- xtable(as.data.frame(out), caption = "Agreement between metrics.",
              align = rep("c", 7), digits = 1)
print(out, include.rownames = FALSE, floating = TRUE,
      table.placement = "p", caption.placement = "top", 
      booktabs = TRUE, comment = FALSE, timestamp = NULL)
```
